Trans-dimensional Bayesian Inference and Nested Sampling

### 2015-09-20 Documents/Talk/content.tex
Lensing ref
Pre-talk edits

\begin{frame}[t]{Motivating Problem I}
\begin{itemize}
\item How many sinusoids are in this data?
\item {\it Note that this must depend on what we believe about their properties,
particularly the amplitudes}
\end{itemize}
\begin{center}
\includegraphics[scale=0.35]{sinewave_data.pdf}
\end{center}
\end{frame}

@@

The only difference between data analysis methods is what prior information
they assume, and what numerical methods are used to calculate the result.
\end{frame}

@@

\begin{frame}[t]{References}
\begin{itemize}
\item Diffusive Nested Sampling (0912.2380)
\item Birth-death MCMC in DNS (1411.3921)
\item Radial Velocity Data (1501.06952)
\item Probabilistic Catalogs (1211.5805)
\item Magnetar Variability (1501.05251)
\end{itemize}
\end{frame}

\begin{frame}[t]{Software}
Everything I've discussed today is GPLd and is on Github.
\end{frame}

>>>>

\begin{frame}[t]{Motivating Problem I}
\begin{itemize}
\item How many sinusoids are in this data?
\item {\it This must depend on what we believe about their properties,
particularly the amplitudes}
\end{itemize}
\begin{center}
\includegraphics[scale=0.35]{sinewave_data.pdf}
\end{center}
\end{frame}

@@

The only differences between data analysis methods:\\
\vspace{20pt}
\begin{enumerate}
\item What prior information is assumed\\
\item Which numerical methods are used to calculate the results.
\end{enumerate}
\end{frame}

@@

\begin{frame}[t]{References}
\begin{itemize}
\item Diffusive Nested Sampling (0912.2380)
\item Birth-death MCMC in DNS (1411.3921)
\item Radial Velocity Data (1501.06952)
\item Probabilistic Catalogs (1211.5805)
\item Magnetar Variability (1501.05251)
\item Strong gravitational lensing (1508.00662)
\end{itemize}

Everything I've discussed today is GPLd and is on Github.
\end{frame}
